Reviving the Lost Art of Combinator Graph Reduction

### 2023-01-01 experiments/superg/doc/paper/paper.tex
JIT call instructions.

\section{TIGRE}
\label{sec:tigre}
\textbf{TODO}

>>>>

\section{TIGRE}
\label{sec:tigre}
\subsection*{Eliminating tags}
Tags are commonly used to distinguish pointers, combinators and literal values.
We get rid of the literal value tag by making all literals go through an indirection node, and introducing a special \texttt{LIT} combinator for such indirection nodes.
To determine if a right-hand side is a literal, we can check for the \texttt{LIT} combinator rather than a tag.
In the TIGRE paper, there is also a pointer and combinator tag, but with Miranda's design, this is not necessary.
If we insist, that final tag value can be put as the lowest bit in the pointer value, since a pointer is typically aligned to some boundary.
We are working with 32-bit (4-byte) wide values, for which on X86 we can assume 4-byte alignment, giving us 2 bits to play with.

\subsection*{Threaded code interpreter}
We make the nodes themselves executable code.
For nodes that represent the combinators, a pointer to that node is just a pointer to the subroutine that implements the combinator.
For application nodes, they are a jump instruction together with the left node as the target (so the left node is the width of one instruction).
The jump instruction should push the current PC onto the stack, which means the stack now directly represents the spine.

The TIGRE style requires that we make our memory writable and executable, which is problematic in many systems.
It seems to work okay on Linux though, so we can use it.

The instruction to use on X86 is \texttt{call}.
It takes one parameter, which is a PC-relative offset.
When we create a node, we should subtract the target position from the location where we are writing the instruction, and use that as the jump parameter.

The trampolines can be generated or hand-coded ahead of time, so our runtime only needs to assemble \texttt{CALL} instructions.

For combinators, we can generate a trampoline that grabs the arguments from the stack, puts them in registers and calls the rust implementation.

It seems to be a good idea to align nodes at a 16-byte boundary for better jump performance:
https://groups.google.com/g/golang-nuts/c/dhGbgC1pAmA
do not put more than 2 branches in a 16-byte block.

Encoding of the call instruction is \texttt{E8} \textit{rel32}, where \textit{rel32} is a 32-bit (little-endian) offset from the \emph{next} instruction.
\textbf{TODO}
